PM Mungbean meta-analysis

### 2021-01-20 02_Preliminary_analysis.Rmd
Edit duplicate chunk names

Trial mean yields in DMI fungicide treated plots
```{r Yield_DMITrials}
PM_MB_dat %>%
   group_by(trial_ref, location, year)%>%
   summarise(mean_yield = mean(grain_yield.t.ha.*1000),
             minimum_yield = min(grain_yield.t.ha.*1000),
             maximum_yield = max(grain_yield.t.ha.*1000),
             yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))%>%
   arrange(yield_sterr) %>%
   kable(align = 'c',
   caption = "Average yield statistics for DMI fungicide treated plots")

>>>>

Trial mean yields in all fungicide treated plots
```{r Yield_AllTrials}
PM_MB_dat %>%
   group_by(trial_ref, location, year)%>%
   summarise(mean_yield = mean(grain_yield.t.ha.*1000),
             minimum_yield = min(grain_yield.t.ha.*1000),
             maximum_yield = max(grain_yield.t.ha.*1000),
             yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))%>%
   arrange(yield_sterr) %>%
   kable(align = 'c',
   caption = "Average yield statistics for DMI fungicide treated plots")
